\section{UPDATE}
\subsection{(1) Brief synopsis of our project:}
We're looking into file hosting systems such as Dropbox, which are popular tools for remote file storage and backup, collaborative work, and file sharing.
These systems rely on centralized storage, which have inherent privacy issues and present a central point of failure.
One solution to this problem would be to distribute data storage across all users by storing replicas on individual user machines.
Such a distributed file hosting system must handle many things: replication strategy, node departures and failures, reads/writes, etc.
So, given users with dynamic online times (and possible failures), can we provide a distributed file hosting system that allows online reads/writes and high data availability?

\subsection{(2) What have we done:}
  a] We've done literature review on distributed storage systems, available replication/synchronization strategies, and similar work on evaluating the above
    b] We've handled a number of design decisions involving:
          -communication model: TCP sockets
                -architecture: clients with local storage, and a broker network that handles client read/write operations (and necessary replication) and group membership
                      -race conditions: how to handle competing operations/how to order operations, how to lock and unlock and queue requests
                            -failures: how to handle when a node goes offline/crashes, how to update a node upon reentry/recovery
                                  -???evaluation: metrics=availability,network overhead,correctness and parameters=node churn, ???
                                    c] We've implemented:
                                          -client: watches local directory and communicates with broker (pushes/pulls updates)
                                                -broker: communicates with clients, handles updates
                                                
\subsection{(3) Where are we now:}
                                                  a] We're finishing up client-broker communication:
                                                        -synchronization policies, local timestamps, locks
                                                          b] We're designing/building the test environment
                                                          (4) What we would like to discuss:
                                                            a] What to measure?
                                                                  -policies?
                                                                        -vs centralized server?
                                                                          b] How to measure?
                                                                                -availability?
                                                                                      -correctness?
                                                                                            -overhead?
\subsection{last notes}
no two people should init at same time
no other clients to pull from = out of date..ok?
major bug = delay on copy
every client goes offline and deletes everything..who to pull from?
NETWORK PARTITION?
broker dies?

VS DROPBOX
delta sync - no need since it's been done before
